# Registration Survey {-}

This page summarizes the data collected from prospective and actual Bootcamp attendees using a survey that began July 19, 2023.

```{r include=FALSE}
library('tidyverse')
library('ggplot2')
library('dplyr')
library('tidyr')
library('stringr')
library('lubridate')

options(gargle_oauth_email = "rick.o.gilmore@gmail.com")
googledrive::drive_auth()
```

Render date: `r Sys.time()`

Survey link: <https://forms.gle/wPBr9XgXmmzhSszm7>

<iframe src="https://docs.google.com/forms/d/e/1FAIpQLScdIbP8TZrulVC01MQbtQN13iaW1WIjQx86f-wGOpC0F3bxBg/viewform?embedded=true" width="640" height="2489" frameborder="0" marginheight="0" marginwidth="0">Loading…</iframe>

## Gather & Clean {-}

Download.

```{r}
if (!dir.exists('csv')) {
  message("Creating missing `csv/`.")
  dir.create("csv")
}

googledrive::drive_download("Open Science Bootcamp 2023: Registration (Responses)", path = "csv/registrations-2023-07.csv", type = "csv", overwrite = TRUE)
```
Clean.

## Visualize {-}

```{r}
registrations <-
  readr::read_csv("csv/registrations-2023-07.csv", show_col_types = FALSE)

reqistrations_qs <- names(registrations)

registrations_clean <- registrations |>
  dplyr::rename(
    timestamp = "Timestamp",
    confirmed = "Will you attend the Bootcamp on August 9-11, 2023?",
    name = "What is your name?",
    psu_email = "What is your PSU email?",
    dept= "What is your department or unit?",
    position = "What is your current position?",
    email = "Email Address",
    am_sess_1 = "Which of these sessions do you plan to attend?...8",
    am_sess_2 = "Which of these sessions do you plan to attend?...9",
    pm_sess_3 = "Which of these sessions do you plan to attend?...10",
    pm_sess_4 = "Which of these sessions do you plan to attend?...11",
    comments = "Any comments?"
  )


registrations_clean <- registrations_clean |>
  dplyr::mutate(timestamp = lubridate::mdy_hms(timestamp, tz = "America/New_York")) |>
  dplyr::arrange(timestamp) |>
  dplyr::filter(!(name == "mina masoumi"),
                !(name == "Ahmad Khanahmadi")) |>
  dplyr::filter(!(role %in% c("duplicate"))) |>
  dplyr::select(-psu_email)
```

### Registration numbers {-}

```{r}
registration_yes <- registrations_clean |> 
  dplyr::filter(confirmed == "Yes") 
```

As of `r Sys.time()`, we have $n=$ `r dim(registration_yes)[1]` confirmed attendees. That is `r round(100*dim(registration_yes)[1]/75, 1)` \% of our target registration/attendance limit of $n=75$, and includes the $n=$ `r registration_yes |> dplyr::filter(role == "staff") |> dplyr::select(name) |> count()` presenters.

### Time series {-}

```{r registrations-timeseries, fig.cap = "Time series of registrations"}
registrations_clean |>
  dplyr::group_by(confirmed) |>
  dplyr::mutate(resp_index = seq_along(confirmed)) |>
  dplyr::ungroup() |>
  ggplot() +
  aes(x = timestamp, y = resp_index, color = confirmed) +
  geom_point() +
  geom_line() +
  facet_grid(~ confirmed) +
  theme(axis.text.x = element_text(angle = 90)) +
  labs(x = NULL, y = 'n') +
  scale_color_manual(breaks = c("No", "Yes"),
                        values=c("red", "green")) +
  theme(legend.position = "none")
```

### By position {-}

```{r by-position, fig.cap="Registrations by position"}
registration_yes |>
  ggplot() +
  aes(x = position, fill = position) +
  geom_bar() +
  theme(legend.position = "none") +
  coord_flip()
```

### By Department & College {-}

```{r by-dept, fig.cap="Registrations by department and college"}
registration_yes <- registration_yes |>
  dplyr::mutate(
    dept = dplyr::recode(
      dept,
      `Clinical Psychology` = "Psychology",
      `Psychology (Cognitive)` = "Psychology",
      `Psychology / SSRI` = "Psychology",
      `Department of Psychology` = "Psychology",
      `English language` = "English",
      `english` = "English",
      `English Language Teaching` = "English",
      `English Department` = "English",
      `Languages` = "Global Languages & Literatures",
      `Languages and Literature` = "Global Languages & Literatures",
      `Department of Foreign Languages` = "Global Languages & Literatures",
      `Linguistics` = "Applied Linguistics",
      `Human Development and Family Studies & Social Data Analytics` = "HDFS",
      `Human Development and Family Studies` = "HDFS",
      `Department of Human Development and Family Studies` = "HDFS",
      `HDFS/DEMO` = "HDFS",
      `RPTM` = "Recreation, Park, & Tourism Management",
      `Spanish Italian and portuguese` = "Spanish, Italian, & Portuguese",
      `Spanish, Italian, and Portuguese Department` = "Spanish, Italian, & Portuguese",
      `Nutrition` = "Nutritional Sciences",
      `College of IST` = "IST",
      `Statistics Department` = "Statistics",
      `Recreation, Park and Tourism Management` = "Recreation, Park, & Tourism Management",
      `SHS` = "Student Health Svcs"
    )
  ) |> 
  dplyr::mutate(
    college = case_match(
      dept,
      "Statistics" ~ "ECoS",
      "Psychology" ~ "CLA",
      "Spanish, Italian, & Portuguese" ~ "CLA",
      "Research Informatics and Publishing" ~ "Libraries",
      "Political Science" ~ "CLA",
      "Applied Linguistics" ~ "CLA",
      "Global Languages & Literatures" ~ "CLA",
      "English" ~ "CLA",
      "C-SoDA" ~ "CLA",
      "Office of Digital Pedagogies and Initiatives" ~ "CLA",
      "IST" ~ "IST",
      "Engineering Science and Mechanics" ~ "Engineering",
      "Chemical Engineering" ~ "Engineering",
      "Material Science and Engineering" ~ "Engineering",
      "Nutritional Sciences" ~ "HHD",
      "HDFS" ~ "HHD",
      "Kinesiology" ~ "HHD",
      "Recreation, Park, & Tourism Management" ~ "HHD",
      "Bellisario College of Communication" ~ "Comm",
      "Marketing" ~ "Smeal"
    ),
    .default = "Unknown",
    .missing = "Unknown"
  )
```

```{r regisrations-timeseries, fig.cap="Registrations by department and college"}
registration_yes |>
  dplyr::filter(!is.na(dept)) |>
  ggplot() +
  aes(x = dept, fill = college) +
  geom_bar() +
  theme(legend.position = "bottom") +
  coord_flip()
```

```{r, include = FALSE}
xtabs(~ college, registration_yes)
```

### [Thu AM Session 1](#day_2_am_session_1) {-}

```{r am_sess_1}
registration_yes |>
  dplyr::filter(!is.na(am_sess_1)) |>
  ggplot() +
  aes(x = am_sess_1, fill = am_sess_1) +
  geom_bar() +
  theme(legend.position = "none") +
  coord_flip() 
```

### [Thu AM Session 2](#day_2_am_session_2) {-}

```{r am_sess_2}
registration_yes |>
  dplyr::filter(!is.na(am_sess_2)) |>
  ggplot() +
  aes(x = am_sess_2, fill = am_sess_2) +
  geom_bar() +
  theme(legend.position = "none") +
  coord_flip()
```

### [Thu PM Session 3](#day_2_pm_session_3) {-}

```{r pm_sess_3}
registration_yes |>
  dplyr::filter(!is.na(pm_sess_3)) |>
  ggplot() +
  aes(x = pm_sess_3, fill = pm_sess_3) +
  geom_bar() +
  theme(legend.position = "none") +
  coord_flip()
```

### [Thu PM Session 4](#day_2_pm_session_4) {-}

```{r pm_sess_4}
registration_yes |>
  dplyr::filter(!is.na(pm_sess_4)) |>
  ggplot() +
  aes(x = pm_sess_4, fill = pm_sess_4) +
  geom_bar() +
  theme(legend.position = "none") +
  coord_flip()
```

<!-- ## Comments {-} -->

<!-- ```{r} -->
<!-- registration_yes |> -->
<!--   dplyr::select(comments) |> -->
<!--   dplyr::filter(!is.na(comments)) |> -->
<!--   knitr::kable(format = 'html') |> -->
<!--   kableExtra::kable_material() -->
<!-- ``` -->
